---
title: "Clean data frame"
author: "Robin"
date: "02/06/2019"
output: html_document
---

```{r}
# User parameters
min_age = 0
max_age = 40
```


# Where do you want to save data?
```{r}
out_dir = '/Users/sifre002/Box/sifre002/9_ExcelSpreadsheets/Dancing_Ladies/clean_data/'
file_name = 'cleaned_multilevel_data'
```

```{r message=FALSE, warning=FALSE, echo=FALSE}
library(readxl)
library(dplyr)
library(sm)
library(lme4)
library(ggplot2)
library(MuMIn)
library(bbmle)
library(gtools)
library(tuple)
```

# Read data
```{r}
Master=read_excel("/Users/sifre002/Box/Dancing Ladies share/IndividualData/Script outputs/Master_MFDFA_DL.xlsx")
precisionInfo = read.csv('/Users/sifre002/Documents/Code/fractal-eye-analyses/out/calibration_verification.csv')
cohort_info=read.csv('/Users/sifre002/Box/Dancing Ladies share/IndividualData/Mullens_DL_lorisMatch_20190103.csv', stringsAsFactors = FALSE)
aoi_data<- read.csv("/Users/sifre002/Box/sifre002/9_ExcelSpreadsheets/Dancing_Ladies/aoi_data/2019_01_10_groupAoiData.txt", sep = '\t')
# demographic data
#Read in information on participant's sex, and combine 
info1=read_excel("/Users/sifre002/Desktop/Elab Master Linking File.xlsx", sheet = 'JE NUMBERS')
info2=read_excel("/Users/sifre002/Desktop/Elab Master Linking File.xlsx", sheet = 'MNBCP NUMBERS')
info3=read_excel('/Users/sifre002/Box/Dancing Ladies share/IndividualData/Pheno Screening Master Linking File.xlsx');
```


```{r}
# Format MFDFA output 
#########################
#import MFDFA output
#########################
Master=read_excel("/Users/sifre002/Box/Dancing Ladies share/IndividualData/Script outputs/Master_MFDFA_DL.xlsx")
Master=as.data.frame(Master) 
# Fix header for easier programming 
colnames(Master)[colnames(Master)=="Longest Fix Duration"] <- "LongestFixDuration"
colnames(Master)[colnames(Master)=="Prop Interp"] <- "PropInterp"
colnames(Master)[colnames(Master)=="Prop Missing"] <- "PropMissing"
colnames(Master)[colnames(Master)=="Movie Name"] <- "MovieName"
colnames(Master)[colnames(Master)=="Segment Num"] <- "Seg"
# Filter out participants who are outside of age range & keep track of who we are missing Age for 
# Master_NAage=Master%>% 
#   filter(is.na(Age))
# Master_old=Master%>%
#   filter(Age>max_age)
Master=Master%>%
  filter(Age>min_age & Age<max_age)

# Create variable for Participant ID (currently combined with session #)
Master=Master%>%
  mutate(Participant= paste( sapply(strsplit(ID, '_'), '[', 1), sapply(strsplit(ID, '_'), '[', 2), sep = '_') )
Master$Age=as.numeric(Master$Age)

```

```{r}
# Clean demographic info 
sexList = rbind(info1 %>% dplyr::select(ID = `SS-ID`, Sex =Subject_Sex),
                info2 %>% dplyr::select(ID = `SS-ID`, Sex =Subject_Sex),
                info3 %>% dplyr::select(ID = `SS-ID`, Sex =Subject_Sex) )
sexList = sexList %>% mutate( Participant = 
                                paste( sapply(strsplit(sexList$ID, '_'), '[', 1), sapply(strsplit(sexList$ID, '_'), '[', 2), sep = '_') )
# Read in lo
cohort_info=read.csv('/Users/sifre002/Box/Dancing Ladies share/IndividualData/Mullens_DL_lorisMatch_20190103.csv', stringsAsFactors = FALSE)
cohort_info=cohort_info%>%
  dplyr::select(ID,cohort_LORIS) %>%
  mutate(Participant= paste( sapply(strsplit(ID, '_'), '[', 1), sapply(strsplit(ID, '_'), '[', 2), sep = '_') ) %>%
  arrange(Participant)

```


Read in data
```{r}

aoi_data = aoi_data %>% filter(longestFix_Dur != -9999)
```


Merge cohort information & remove Babarr (they were recruited differently)
```{r}
cohort=merge(Master, cohort_info, by="Participant", all=FALSE,sort=FALSE)
cohort= unique( cohort[ , c("Participant","cohort_LORIS") ] )
Master2=merge(Master, cohort, by="Participant", all.x=TRUE)
Master2$cohort=Master2$cohort_LORIS
# Combine sub-cohorts to create broader ones 
Master2$cohort_collapsed = Master2$cohort
Master2$cohort_dummy = NA
Master2[grepl('A', Master2$cohort), 'cohort_collapsed'] = 'BCP' 
Master2[grepl('B', Master2$cohort), 'cohort_collapsed'] = 'BCP' 
Master2[grepl('C', Master2$cohort), 'cohort_collapsed'] = 'BCP' 
Master2[grepl('D', Master2$cohort), 'cohort_collapsed'] = 'BCP' 
Master2[grepl('E', Master2$cohort), 'cohort_collapsed'] = 'BCP' 
Master2[grepl('BABARR', Master2$cohort), 'cohort_collapsed'] = 'Babarr' # Remove Babarr, bc they were recruited differently 
Master2[grepl('BSLERP', Master2$cohort), 'cohort_collapsed'] = 'Bslerp' 
Master2[grepl('DevSocAtt', Master2$cohort), 'cohort_collapsed'] = 'DSA_CS'  
# Create numeric versions of variables 
Master2[grepl('BCP', Master2$cohort_collapsed), 'cohort_dummy'] = 1
Master2[grepl('Bslerp', Master2$cohort_collapsed), 'cohort_dummy'] = 2
Master2[grepl('DSA_CS', Master2$cohort_collapsed), 'cohort_dummy'] = 3
Master2[grepl('Babarr', Master2$cohort_collapsed), 'cohort_dummy'] = 4
Master2 = Master2 %>% filter(cohort_dummy !=4) # Remove Babarr, bc they were recruited differently 
```

Clean AOI data
```{r}
aoi_data2 = aoi_data %>%
  dplyr::select(ID = id, 
                MovieName = movie,
                Seg = seg, 
                longestFix_aoi = longestFix_Dur, faceCount, otherCount)
```


Merge Sex information 
```{r}
# Merge sex list and Master 
sexList = sexList %>% dplyr::select(Participant, Sex)
sexList[sexList$Participant == 'JE000211_04', 'Participant'] ='JE000211_03' # error in master linkning file
sexList[sexList$Participant == 'MNBCP000139_04', 'Participant'] ='MNBCP000139_05' # error in master linkning file
sex=merge(Master2, sexList, by="Participant", all=FALSE,sort=FALSE)
sex= unique( sex[ , c("ID","Sex") ] )

Master2=merge(Master2, sex[ , c("ID","Sex")], by="ID", all.x=TRUE)
Master2$female = NA
Master2[Master2$Sex == 'F' & !is.na(Master2$Sex), 'female'] = 1 # Female as reference group for modelling
Master2[Master2$Sex == 'M' & !is.na(Master2$Sex), 'female'] = 0
```

Add stimulus type (i.e., CalVer, Pixelated, NonPixelated) to MFDFA dataframe  
```{r}
Master2$Calver = ifelse(grepl('Center|Left|Right', Master2$MovieName), 1, 0)
Master2$Pixelated = ifelse(grepl('S', Master2$MovieName), 1, 0)
Master2$NonPixelated = ifelse(Master2$Pixelated == 0 & Master2$Calver == 0, 1, 0)
```

Creates a FinalCalVer dataframe of average calibration XY precision information for each kid who made it through CalVer processing
```{r}
CalVerMaster=precisionInfo
#Find average XY precision for each calibration point
CalVerMaster=CalVerMaster%>%
  filter(!is.na(CoordX)) %>%
  mutate(Precision_RMS_X_Y=(PrecRMSx + PrecRMSy)/2) %>%
  select(ID=X, Precision_RMS_X_Y, Stimulus)
#Establishes 2 SD cutoffs for acceptable precision values
PrecSD=sd(CalVerMaster$Precision_RMS_X_Y, na.rm=TRUE)
cutoff=mean(CalVerMaster$Precision_RMS_X_Y, na.rm=TRUE)+2*PrecSD

#Creates exclude/include dummies based on cutoff
CalVerMaster=CalVerMaster%>%
  mutate(include=if_else(Precision_RMS_X_Y<cutoff,1,0)) 

#Excludes points above precision cutoff AND those without any precision info
FinalCalVer=CalVerMaster%>% 
  filter(include==1) #only includes pts with good precision

#Finds number of participants remaining
#N=unique(FinalCalVer$ID)

#Groups by ID to get average precision info for each remaining participant
FinalCalVer=FinalCalVer%>%
  group_by(ID)%>%
  summarise(AvgPrecision=mean(Precision_RMS_X_Y))%>%
  filter((!is.na(ID)))
```

```{r}
# Commented out code - useful for reporting purposes
# Master_sum=Master2%>%
#   group_by(Participant, ID)%>% 
#   summarise(n())%>%
#   mutate(dummy = 1)%>%
#   group_by(Participant)%>%
#   summarise(sessions=sum(dummy))
```


Add individual precision info FROM FINALCALVER to MFDFA & includes only those w/ precision data in FinalCalvr  
```{r message=FALSE, warning=FALSE, echo=FALSE}
colnames(FinalCalVer)[colnames(FinalCalVer)=="AvgPrecision"] <- "PrecisionRMS_X_Y"
FinalCalVer$precisionInfo = 1
Master3 = merge(Master2,FinalCalVer, by="ID", all.x=TRUE)
Master_precInf=Master3%>%
  filter(precisionInfo==1)
# Useful for reporting purposes 
#a=unique(Master_precInf$ID)
#a=unique(as.character(Master_precInf$Participant))

#Filters out those without precision info (i.e., did not make it through CalVer/did not have any points above quality thresholds from previous code)
Master3=Master3%>%
  filter(precisionInfo==1)
#a=unique(Master$ID) #131

#Center precision on grand mean (will use this for modelling)
avePrec=mean(Master3$PrecisionRMS_X_Y)
Master3=Master3%>%
  mutate(PrecisionRMS_X_Y_centered=PrecisionRMS_X_Y-avePrec)
```

Establishes cutoff levels for acceptable amount missing/interpolated for each segment
```{r}
#Finds 80th quantile for amount interpoloated and missing levels based on entire sample
MasterInterpC=quantile(Master3$PropInterp, .80)
# MasterMissingC=quantile(Master3$PropMissing %>% select(), .80) got rid of this bc we have longest fix as a covariate 

Master_too_much_interp=Master3%>%
  filter(PropInterp>MasterInterpC)
# Master_too_much_missing=Master3%>%
#   filter(PropMissing>MasterMissingC)
#Master_combo=rbind(Master_too_much_interp,Master_too_much_missing)
#a=as.data.frame(unique(Master_combo$ID))#251
#Selects only segments with acceptable missing/interp levels
Master3=Master3%>%
  filter(PropInterp<MasterInterpC)
```

Examines and removes missing H's
```{r}
#Identifies segments too short to calculate H
Master_too_short=Master3%>% 
  filter(H=="Too Short")
#a=as.data.frame(unique(Master_too_short$ID))

#Identifies segments for which H could not be calculated for unknown reasons (e.g., dividing by 0 in matlab code)
Master_NA=Master3%>% #628
  filter(is.na(H))
#a=unique(Master_NA$ID)
#Master_no_H=rbind(Master_too_short, Master_NA)

#Makes all non-numeric values Na, selecting only segments w/ valid H's
Master3$H=as.numeric(Master3$H)
Master3=subset(Master3, !is.na(H))
a=unique(Master3$Participant) #184 --loss of 11 infants
a=as.data.frame(unique(Master3$ID)) #376 --loss of 45 visits

#Extracts pertinent info for modeling
# MasterSum=Master3%>%
#   group_by(ID)%>%
#   dplyr::select(ID, Participant, LongestFixDuration, PropInterp, PropMissing, PrecisionRMS_X_Y,Amplitude, H, Age, MovieName,Stimulus, Version, Pixelated, NonPixelated, CalVer, Stimulus,Sex, female, cohort)
# 
# MasterSum=as.data.frame(MasterSum)
# 
# MasterSum$Stimulus=as.factor(MasterSum$Stimulus)
# MasterSum$Age=as.numeric(MasterSum$Age)
```

Merge aoi data with master_longit
```{r}
Master_longit = Master3 %>%
  dplyr::select(ID, Participant, LongestFixDuration, PropInterp, PropMissing, PrecisionRMS_X_Y,Amplitude, H, SpectWidth, Age, MovieName, Seg, Stimulus, Version, Pixelated, NonPixelated, Calver, Stimulus,Sex, female, cohort_dummy)
temp1 = Master_longit %>% filter(Stimulus=='DL') # only movie trials
temp2 = Master_longit %>% filter(Stimulus=='C') # only CalVer trials

test =merge(temp1, aoi_data2, by = c('ID', 'MovieName', 'Seg'))
test$propFace_seg = test$faceCount / (test$faceCount + test$otherCount)

temp2$longestFix_aoi = NA
temp2$faceCount = NA
temp2$otherCount = NA
temp2$propFace_seg = NA

Master_longit2 = rbind(test, temp2)
```


# Create person-, visit-, and movie-centered variables. These are used to parse variance for modelling.
```{r}
# Get grand mean for average age
AveAge = Master_longit2 %>%
  group_by(ID)%>%
  summarise(Age = unique(Age)) %>%
  summarise(Age = mean(Age) )

# Get grand mean for average longest fix
aveLongFix=mean(Master_longit2$LongestFixDuration)
AveAge = Master_longit2 %>%
  group_by(ID) %>%
  summarise(age = mean(Age))
AveAge = mean(AveAge$age)
#avePrec=mean(Master_longit2$PrecisionRMS_X_Y)
#avePropFace = mean(Master_longit2$propFace_seg, na.rm = TRUE)

#
Master_longit2=Master_longit2%>%
  mutate(Age_centeredGrandmean=as.numeric(Age-AveAge),
         longestFix_seg_centeredGrandmean = as.numeric(LongestFixDuration - aveLongFix))

# Creating level 3 (person) variables:
# Average age: Participant's average age, centered on grand mean
# Average Interpolated: mean prop interp
# Average precision: mean precision (weight each visit once)
# Average longest fix: mean longest fix, centered on grand mean 
# Average face looking: NEED TO ADD THIS 
personLevel_var=Master_longit2%>%
  group_by(Participant)%>%
  summarise(AveAge_person=mean(unique(Age_centeredGrandmean)), 
            AveInterp_person=mean(PropInterp),
            AveMissing_person=mean(PropMissing),
            AvePrecision_person = mean(PrecisionRMS_X_Y),
            AveLongestFix_person=mean(longestFix_seg_centeredGrandmean),
            AvePropFace_person = sum(faceCount, na.rm = TRUE) / ( sum(faceCount, na.rm = TRUE) + sum(otherCount, na.rm = TRUE) ),
            n_person=n())

# Session age = Age_centeredGrandmean (no within-session variability)
# Average interpolated: Mean prop interp, for the session
# Average Missing: Mean prop Missing
# Average longest fix: mean longest fix, centered on grand mean
# Average face looking: mean face looking for the session 
sessionLevel_var = Master_longit2 %>%
  group_by(ID) %>%
  summarise(AveInterp_session = mean(PropInterp),
            AveMissing_session = mean(PropMissing), 
            AveLongestFix_session = mean(longestFix_seg_centeredGrandmean),
            AvePropFace_session = sum(faceCount, na.rm = TRUE) / ( sum(faceCount, na.rm = TRUE) + sum(otherCount, na.rm = TRUE) ))


movieLevel_var = Master_longit2 %>%
  group_by(Participant, ID, MovieName) %>%
  summarise(AveInterp_movie = mean(PropInterp),
            AveMissing_movie = mean(PropMissing), 
            AveLongestFix_movie = mean(longestFix_seg_centeredGrandmean),
            AvePropFace_movie = sum(faceCount, na.rm = TRUE) / ( sum(faceCount, na.rm = TRUE) + sum(otherCount, na.rm = TRUE) ))

# Merge person-level
Master_longit3 = merge(Master_longit2, personLevel_var, by = 'Participant')
# Merge visit-level
Master_longit4 = merge(Master_longit3, sessionLevel_var, by = 'ID')
# Merge movie-level
Master_longit5 = merge(Master_longit4, movieLevel_var, by = c('Participant', 'ID', 'MovieName'))
# Create SEGMENT-LEVEL VARIABLES centered at MOVIE LEVEL
Master_longit5$propInterp_segment_groupmeancentered = Master_longit5$PropInterp - Master_longit5$AveInterp_movie
Master_longit5$longestFix_segment_groupmeancentered = Master_longit5$longestFix_seg_centeredGrandmean - Master_longit5$AveLongestFix_movie
Master_longit5$propFace_segment_groupmeancentered = Master_longit5$propFace_seg - Master_longit5$AvePropFace_movie

# Create MOVIE-LEVEL VARIABLES centered at VISIT-LEVEL
Master_longit5$propInterp_movie_groupmeancentered = Master_longit5$AveInterp_movie - Master_longit5$AveInterp_session
Master_longit5$longestFix_movie_groupmeancentered = Master_longit5$AveLongestFix_movie - Master_longit5$AveLongestFix_session
Master_longit5$propFace_movie_groupmeancentered = Master_longit5$AvePropFace_movie - Master_longit5$AvePropFace_session

# Create VISIT-LEVEL variables centered at PERSON-LEVEL
Master_longit5$propInterp_session_groupmeancentered = Master_longit5$AveInterp_session - Master_longit5$AveInterp_person
Master_longit5$longestFix_session_groupmeancentered = Master_longit5$AveLongestFix_session - Master_longit5$AveLongestFix_person
Master_longit5$propFace_session_groupmeancentered = Master_longit5$AvePropFace_session - Master_longit5$AvePropFace_person
Master_longit5$precision_session_groupmeancentered = Master_longit5$PrecisionRMS_X_Y - Master_longit5$AvePrecision_person

# Create PERSON_LEVEL variables centered at GRAND MEAN
Master_longit5$propInterp_person_grandmeancentered = Master_longit5$AveInterp_person - mean(Master_longit5$PropInterp)
Master_longit5$longestFix_person_grandmeancentered  = Master_longit5$AveLongestFix_person - mean(Master_longit5$AveLongestFix_person)
Master_longit5$propFace_person_grandmeancentered  = Master_longit5$AvePropFace_person - mean(Master_longit5$propFace_seg, na.rm = TRUE)
Master_longit5$precision_person_grandmeancentered  = Master_longit5$AvePrecision_person - mean(Master_longit5$PrecisionRMS_X_Y, na.rm=TRUE)

############################################################################
#Commented out code - could be useful or reporting 

#Finds participant info
# Master_longit_sample=Master_longit4%>%
#   group_by(Participant, ID)%>%
#   summarise(n=n(),
#             female=mean(as.numeric(female, na.rm=TRUE)))
# Master_longit_female=Master_longit4%>%
#   filter(female==1)%>%
#   group_by(Participant)%>%
#   summarise(n=n())

# N_female=unique(Master_longit_female$Participant)
# mean(Master_longit$PropMissing, na.rm=TRUE)

# #Finds time pts per kid
# library(tuple)
# Master_longit_sum=Master_longit%>%
#   group_by(Participant, ID)%>%
#   summarize(n())%>%
#   mutate(dummy=1)%>%
#          # dup=duplicated(Participant),
#          # trip=triplicated(Participant))%>%
#   group_by(Participant)%>%
#   summarize(sessions=sum(dummy))

```

<!-- Sanity checking  -->
<!-- ```{r} -->
<!-- model_data = Master_longit5 %>% filter(Stimulus == 'DL') -->

<!-- ggplot(data = model_data, aes(x = Age, y = H) ) + -->
<!--   stat_smooth(method = 'lm', se = FALSE,  formula = y~x, show.legend = FALSE, aes(group = MovieName, color = MovieName)) + -->
<!--   stat_smooth(method ='lm', formula = y~x, color = 'black') -->

<!-- library(psychometric) -->
<!-- ICC1.lme(H, MovieName, model_data)   -->

<!-- ``` -->

Save data 
```{r}
write.csv(file = paste(out_dir, file_name, '.csv', sep= ''), Master_longit5)
```



