---
title: "Model relationship between face-looking and H"
author: "Robin"
date: "02/06/2019"
output: html_document
---

```{r message=FALSE, warning=FALSE, echo=FALSE}
library(readxl)
library(dplyr)
library(sm)
library(lme4)
library(ggplot2)
library(MuMIn)
library(AICcmodavg)
library(bbmle)
library(glmmTMB)
library(lmerTest)
library(psychometric)
library(texreg)
```

Import clean data 
```{r}
data = read.csv('/Users/sifre002/Box/sifre002/9_ExcelSpreadsheets/Dancing_Ladies/clean_data/cleaned_multilevel_data.csv')
model_data = data %>% filter(Stimulus == 'DL')
model_data$Pixelated = as.factor(model_data$Pixelated)
```

# Visualizations
Visualize if looking at faces predicts H 
```{r}
# Segment-level face looking vs H
ggplot(data=model_data, aes(x=propFace_seg, y=H) ) +
  geom_point(alpha = .3) + 
  geom_smooth(method = 'loess') +
  scale_x_continuous(breaks = c(0, .2, .4, .6, .8, 1)) +
  ylab('Complexity (h)') +
  xlab('Proportion looking at face, segment level') +
  facet_wrap(~Pixelated)
# Movie-level face looking vs H
ggplot(data=model_data, aes(x=model_data$AvePropFace_movie, y=H) ) +
  geom_point(alpha = .3) + 
  geom_smooth(method = 'loess') +
  scale_x_continuous(breaks = c(0, .2, .4, .6, .8, 1)) +
  ylab('Complexity (h)') +
  xlab('% Face looking @ Visit level, relative to H') +
  facet_wrap(~Pixelated)
# Session-level face looking vs H
ggplot(data=model_data, aes(x=model_data$AvePropFace_session, y=H) ) +
  geom_point(alpha = .3) + 
  geom_smooth(method = 'loess') +
  scale_x_continuous(breaks = c(0, .2, .4, .6, .8, 1)) +
  ylab('Complexity (h)') +
  xlab('% Face looking @ Visit level, relative to H') +
  facet_wrap(~Pixelated)
# Person-level face looking vs H 
ggplot(data=model_data, aes(x=AvePropFace_person, y=H) ) +
  geom_point(alpha = .3) + 
  geom_smooth(method = 'loess') +
  scale_x_continuous(breaks = c(0, .2, .4, .6, .8, 1)) +
  ylab('Complexity (h)') +
  xlab('% Face looking @ Person level, for all of their visits')+
  facet_wrap(~Pixelated)
```

Visualize age-related change in % face looking looking
```{r}
ggplot(data=model_data, aes(x = Age, y=propFace_seg) ) +
  geom_point(alpha = .3) + 
  geom_smooth(method = 'loess') +
  scale_x_continuous(breaks = c(3,5,9,15,18,24,36)) +
  xlab('Age') +
  facet_wrap(~Pixelated)
```

Face-looking (over time) models
Logistic regression 
glmer, family = 'binomial'
cbind(n times on task, n time not on task)... allows things to differ between kids
if 0 is inflated by the condition, then you dont need to worry about zero inflation 
```{r}
y = cbind(model_data$faceCount, model_data$otherCount)
e = log(1)
#################################
# Functional form 
#################################
# FE and RE for intercept 
glm.0 = glmer(y ~ (1|Participant),
    data = model_data, family = 'binomial')
# FE of age 
glm.1 = glmer(y ~ 1 + Age_centeredGrandmean + (1|Participant),
    data = model_data, family = 'binomial')
glm.2 = glmer(y~ 1 + Age_centeredGrandmean + (1+Age_centeredGrandmean|Participant),
    data = model_data, family = 'binomial')
mynames <- as.character (c("glm.0", "glm.1", "glm.2")) # model numbers as characters
myaicc  <- ICtab(logLik(glm.0),
		     logLik(glm.1), logLik(glm.2), 
		     type ="AICc",
		     nobs = nrow(na.omit(model_data)),
		     weights =TRUE,delta =TRUE,sort=TRUE,mnames=mynames,base=TRUE)
myaicc$rweight <- max(myaicc$weight)/myaicc$weight
myaicc # Linear RE and FE of age

#################################
# Covariates & main effects
#################################
# Adding covariates (calver precision is not critical to include here)
glmer.3 = glmer(y~ 1 + Age_centeredGrandmean + 
                     AveAge_person +
                 # QC - longest fix 
                    scale(LongestFixDuration) +
                   Sex +
                   (1+Age_centeredGrandmean|Participant),
    data = model_data, family = 'binomial')
summary(glmer.3a)

# Add Pix
glmer.4 = glmer(y~ 1 + Age_centeredGrandmean + 
                     AveAge_person +
                 # QC - longest fix 
                    scale(LongestFixDuration) +
                   Sex +
                    Pixelated +
                   (1+Age_centeredGrandmean|Participant),
    data = model_data, family = 'binomial')


glmer.5 = glmer(y~ 1 + Age_centeredGrandmean + 
                     AveAge_person +
                 # QC - longest fix 
                    scale(LongestFixDuration) +
                   Sex +
                    Pixelated + Age_centeredGrandmean:Pixelated + 
                   (1+Age_centeredGrandmean|Participant),
    data = model_data, family = 'binomial')
mynames <- as.character (c("glm.3", "glm.4", "glm.5")) # model numbers as characters
myaicc  <- ICtab(logLik(glmer.3),
		     logLik(glmer.4), logLik(glmer.5), 
		     type ="AICc",
		     nobs = nrow(na.omit(model_data)),
		     weights =TRUE,delta =TRUE,sort=TRUE,mnames=mynames,base=TRUE)
myaicc$rweight <- max(myaicc$weight)/myaicc$weight
myaicc # Linear RE and FE of age
# Model with Age x Pix interaction is best fit

summary(glmer.5)

```

- For the average segment, participants are more likely to look at non-face AOIs than face AOIs.  
- Probability=1 / (1 + exp(-x)) 
```{r}
# pix effect --> 14% increase
1/(1+exp(--1.7813259))

# pix x age interaction
1/(1+exp(-0.0126261))
```



# Modelling 
Establishing functional form - Best fitting model inclues Linear effect of age
```{r}
#Establishing functional form 
# Intercept: FE, and RE for Person and Visit
lmer.0=lmer(H~1+(1|Participant)+(1|ID)+(1|MovieName), data=model_data, REML=FALSE) 
# 
lmer.1=lmer(H~1+Age_centeredGrandmean+(1|Participant)+(1|ID)+(1|MovieName), data=model_data, REML=FALSE) #linear age,  

lmer.2=lmer(H~1+Age_centeredGrandmean+(1+Age_centeredGrandmean|Participant)+(1|ID)+(1|MovieName), data=model_data, REML=FALSE) #linear age, FE and RE

mynames <- as.character (c("lmer.1", "lmer.2")) # model numbers as characters

myaicc  <- ICtab(logLik(lmer.1),
		     logLik(lmer.2),
		     type ="AICc",
		     nobs = nrow(na.omit(model_data)),
		     weights =TRUE,delta =TRUE,sort=TRUE,mnames=mynames,base=TRUE)
myaicc$rweight <- max(myaicc$weight)/myaicc$weight
myaicc #dAICc over 2 means significantly better

anova(lmer.2, lmer.1) # Model with FE and RE for age fits the data better 

# Add quadratic FE for age 
lmer.3=lmer(H ~ 1 + Age_centeredGrandmean + I(Age_centeredGrandmean^2)+
              (1+Age_centeredGrandmean|Participant) + (1|ID) +(1|MovieName),
            data=model_data, REML=FALSE) #quad age
anova(lmer.3, lmer.2) # Does not improve our model 
# Commented out code for looking at variance
# total_var = 1.821e-03 +1.273e-03+3.880e-06+7.475e-03
# l1_within_resid = 7.475e-03
# l2_int_visit =1.821e-03
# l3_int_partic = 1.273e-03
# l3_age = 3.880e-06
# 
# l1_within_resid / total_var # Within-person 70% of variance explained
```
We adopt a linear FE and RE of age. 

Adding in QC covariates
```{r}
# Add in all covariates
lmer.3a = lmer(H~1+Age_centeredGrandmean + AveAge_person +
                # QC - prop interp   
                propInterp_segment_groupmeancentered + propInterp_movie_groupmeancentered + 
                 propInterp_session_groupmeancentered +  propInterp_person_grandmeancentered +
                 # QC - longest fix 
                 longestFix_seg_centeredGrandmean + longestFix_movie_groupmeancentered + 
                 longestFix_session_groupmeancentered + longestFix_person_grandmeancentered + 
                 # QC - precision 
                 precision_session_groupmeancentered + precision_person_grandmeancentered + 
                 # cohort dummy
                 as.factor(cohort_dummy) + Sex + 
                (1+Age_centeredGrandmean|Participant) + (1|ID)+(1|MovieName), data=model_data, REML=FALSE)

# We drop: All prop interp variables, all longest fix variables, dummy & cohort
# Node- we keep Average age for substantive reasons.
lmer.3b = lmer(H~1+Age_centeredGrandmean + AveAge_person +
                # QC 
                 precision_session_groupmeancentered + precision_person_grandmeancentered + 
                (1+Age_centeredGrandmean|Participant) + (1|ID)+(1|MovieName), data=model_data, REML=FALSE) 

anova(lmer.3a, lmer.3b) # dropping n.s. covariates does not hurt model fit. We adopt the simpler model (lmer.3b)
```
QC variables retained: AveAge_person + propInterp_session_groupmeancentered + precision_session_groupmeancentered + precision_person_grandmeancentered + as.factor(cohort_dummy)

Effect of Pix
```{r}
# Add Pixelated FE
lmer.4 =  lmer(H~1+Age_centeredGrandmean + AveAge_person +
                # QC 
                 precision_session_groupmeancentered + precision_person_grandmeancentered + 
                # Variables we care about
                Pixelated + 
                (1+Age_centeredGrandmean|Participant) + (1|ID)+(1|MovieName), data=model_data, REML=FALSE) 


# Add pixelated RE at person level. does not converge 
lmer.4b =  lmer(H~1+Age_centeredGrandmean + 
                AveAge_person +
                # QC 
                 precision_session_groupmeancentered + precision_person_grandmeancentered + 
                # Variables we care about
                Pixelated + 
                (1+Age_centeredGrandmean + Pixelated|Participant) + (1|ID)+(1|MovieName), data=model_data, REML=FALSE) 

# Add pixelated RE at visit level
lmer.4c =  lmer(H~1+Age_centeredGrandmean +
                # QC 
                AveAge_person + 
                 precision_session_groupmeancentered + precision_person_grandmeancentered +
                # Variables we care about
                Pixelated + 
                (1+Age_centeredGrandmean|Participant) + (1+Pixelated|ID)+(1|MovieName), data=model_data, REML=FALSE) 


# Add pixelated RE at visit and person level 
lmer.4d =  lmer(H~1+Age_centeredGrandmean +
                # QC 
                AveAge_person + 
                 precision_session_groupmeancentered + precision_person_grandmeancentered + 
                # Variables we care about
                Pixelated + 
                (1+Age_centeredGrandmean+Pixelated|Participant) + (1+Pixelated|ID)+(1|MovieName), data=model_data, REML=FALSE) 

mynames <- as.character (c("lmer.4", "lmer.4b", "lmer.4c", "lmer.4d")) # model numbers as characters

myaicc  <- ICtab(logLik(lmer.4),
		     logLik(lmer.4b), logLik(lmer.4c), logLik(lmer.4d),
		     type ="AICc",
		     nobs = nrow(na.omit(model_data)),
		     weights =TRUE,delta =TRUE,sort=TRUE,mnames=mynames,base=TRUE)
myaicc$rweight <- max(myaicc$weight)/myaicc$weight
myaicc #dAICc over 2 means significantly better
# Random effect of Pix is better mdoel fit  
```
We adopt the model with FE, and RE for Pix at visit-level

Effect of prop face
```{r}
# Add prop face 
lmer.5 =  lmer(H~1+Age_centeredGrandmean +
                # QC 
                AveAge_person + 
                 precision_session_groupmeancentered + precision_person_grandmeancentered + 
                # Variables we care about
                Pixelated + 
                  propFace_segment_groupmeancentered+ propFace_movie_groupmeancentered + propFace_session_groupmeancentered + propFace_person_grandmeancentered +
                (1+Age_centeredGrandmean|Participant) + (1+Pixelated|ID)+(1|MovieName), data=model_data, REML=FALSE) 

anova(lmer.4c, lmer.5)
```
Face looking alone does not predict H. The between-person effect of face-looking is trending (p=.06)

Face x Pixelated interaction
```{r}
# Face:Pixelated interaction

lmer.6 =  lmer(H~1+Age_centeredGrandmean +
                # QC 
                AveAge_person + 
                 precision_session_groupmeancentered + precision_person_grandmeancentered + 
                # Variables we care about
                Pixelated + 
                  propFace_segment_groupmeancentered+ propFace_movie_groupmeancentered + propFace_session_groupmeancentered + propFace_person_grandmeancentered +
                # face: pix
                propFace_segment_groupmeancentered:Pixelated + propFace_movie_groupmeancentered:Pixelated + 
                 propFace_session_groupmeancentered:Pixelated + propFace_person_grandmeancentered:Pixelated +  
                (1+Age_centeredGrandmean|Participant) + (1+Pixelated|ID)+(1|MovieName), data=model_data, REML=FALSE) 

```
There is a significant effect of movie-level face-looking looking on H. There is also an interaction between Pixelated and movie-level face-looking (marginally)

Does age interact with Pixelated, or face-looking? 
```{r}
# Pix:Age interactoin  - n.s.
lmer.7 = lmer(H~1+Age_centeredGrandmean +
                # QC 
                AveAge_person + 
                 precision_session_groupmeancentered + precision_person_grandmeancentered + 
                # Pix
                Pixelated + 
                # Face-looking
                  propFace_segment_groupmeancentered+ propFace_movie_groupmeancentered + propFace_session_groupmeancentered + propFace_person_grandmeancentered +
                # face: pix
                propFace_segment_groupmeancentered:Pixelated + propFace_movie_groupmeancentered:Pixelated + 
                 propFace_session_groupmeancentered:Pixelated + propFace_person_grandmeancentered:Pixelated + 
                # Age x Pix
                Age_centeredGrandmean:Pixelated  + 
                (1+Age_centeredGrandmean|Participant) + (1+Pixelated|ID)+(1|MovieName), data=model_data, REML=FALSE) 

# Age x face:looking - n.s. 
lmer.8 = lmer(H~1+Age_centeredGrandmean +
                # QC 
                AveAge_person +  
                 precision_session_groupmeancentered + precision_person_grandmeancentered + 
                # Pix
                Pixelated + 
                # Face-looking
                  propFace_segment_groupmeancentered+ propFace_movie_groupmeancentered + propFace_session_groupmeancentered + propFace_person_grandmeancentered +
                # face: pix
                propFace_segment_groupmeancentered:Pixelated + propFace_movie_groupmeancentered:Pixelated + 
                 propFace_session_groupmeancentered:Pixelated + propFace_person_grandmeancentered:Pixelated + 
                # Age x face
                Age_centeredGrandmean:propFace_segment_groupmeancentered+ Age_centeredGrandmean:propFace_movie_groupmeancentered  + 
                Age_centeredGrandmean:propFace_session_groupmeancentered+ Age_centeredGrandmean:propFace_person_grandmeancentered +
                (1+Age_centeredGrandmean|Participant) + (1+Pixelated|ID)+(1|MovieName), data=model_data, REML=FALSE) 


```
No significant 2-way interactions between Face-looking:Age, or Pixelated:Age


```{r}
lmer.6 =  lmer(H~1+Age_centeredGrandmean +
                # QC 
                AveAge_person + 
                 precision_session_groupmeancentered + precision_person_grandmeancentered + 
                # Variables we care about
                Pixelated + 
                  propFace_segment_groupmeancentered+ propFace_movie_groupmeancentered + propFace_session_groupmeancentered + propFace_person_grandmeancentered +
                # face: pix
                propFace_segment_groupmeancentered:Pixelated + propFace_movie_groupmeancentered:Pixelated + 
                 propFace_session_groupmeancentered:Pixelated + propFace_person_grandmeancentered:Pixelated +  
                (1+Age_centeredGrandmean|Participant) + (1+Pixelated|ID)+(1|MovieName), data=model_data, REML=FALSE) 

# Removing the interactions at the main-effect of face-looking that was n.s.
lmer.6b =  lmer(H~1+Age_centeredGrandmean +
                # QC 
                AveAge_person + 
                 precision_session_groupmeancentered + precision_person_grandmeancentered + 
                # Variables we care about
                Pixelated + 
                  propFace_segment_groupmeancentered+ propFace_movie_groupmeancentered + propFace_session_groupmeancentered + propFace_person_grandmeancentered +
                # face: pix
                 propFace_movie_groupmeancentered:Pixelated + 
                (1+Age_centeredGrandmean|Participant) + (1+Pixelated|ID)+(1|MovieName), data=model_data, REML=FALSE) 


anova(lmer.6, lmer.6b)
mynames <- as.character (c("lmer.5", "lmer.6", "lmer.6b")) # model numbers as characters

myaicc  <- ICtab(logLik(lmer.5), logLik(lmer.6),
		     logLik(lmer.6b),
		     type ="AICc",
		     nobs = nrow(na.omit(model_data)),
		     weights =TRUE,delta =TRUE,sort=TRUE,mnames=mynames,base=TRUE)
myaicc$rweight <- max(myaicc$weight)/myaicc$weight
myaicc #dAICc over 2 means significantly better
# Random effect of Pix is better mdoel fit  

model_data$yhat1 = predict(lmer.6b, newdata = model_data, re.form = NA) 
#Effect size=18.4% var explained --goes down by 2% w/out miss/interp cutoffs
	R = cor(x = model_data$H, 
              y =(model_data$yhat1), use = "complete.obs")
	
	R^2 #19.5% of var accounted for by the model
```

Make the html table
```{r}

htmlreg(list(lmer.0, lmer.2, lmer.3b, lmer.4c, lmer.6b), 
        digits=3, bold=0.05,include.psuedors=TRUE, doctype = TRUE, 
        caption='Table of Model Evidence for Predicting Longitudinal H Using Likelihood Ratio Tests: NonPix as Reference', 
        caption.above = TRUE, stars = c(0.001, 0.01, 0.05, 0.1))
```

Interpreting beta weights
Standardizing the coefficients
Take mean H at each time point.
Fit Random-intercept model (two-level). within-person variance there is what we use to standardize.
Sqrt(L1 variance) <-- within-person SD aka standardized Y 
Standardized B = .003 / (standardized y).. .. now represents number of SD associated with a month of age-change.

```{r}
5.809e-02*sd(model_data$H)

```



# Examine 2-way interaction
```{r}
model_data$yhat1 = predict(lmer.6b, newdata = model_data, re.form = NA) 
model_data$Pixelated2 = ifelse(model_data$Pixelated==0, 'Social', 'Pixelated')

# Plot effect of face-looking, facet_wrapped on Pix 
ggplot(data = model_data, aes(x = propFace_movie_groupmeancentered, y=yhat1)) + # group_by(age_bin), color = age_bin)
  geom_point(alpha = .3) + 
  geom_smooth(method = 'lm') +
  scale_x_continuous(breaks = c(0, .2, .4, .6)) +
  ylab('Y-hat, Complexity (h)') +
  xlab('Prop face looking movie, Centered on person-mean')  + 
  

ggplot(data = model_data, aes(x = propFace_movie_groupmeancentered, y=yhat1)) + 
  geom_point(alpha = .3, aes(y = H)) + 
  geom_smooth(method = 'glm') +
  scale_x_continuous(breaks = seq(-0.4, 0.6, .2), limits = c(-.4,.4)) +
  ylab('Y-hat, Complexity (h)') +
  xlab('Prop face looking movie, Centered on person-mean')

# ggplot(data = model_data, aes(x = AvePropFace_movie, y=yhat1) ) + # group_by(age_bin), color = age_bin)
#   geom_point(aes(y = H), alpha = .2, color = 'IndianRed') + 
#   geom_smooth(aes(y = yhat1), method = 'lm', color = 'black', se = TRUE) +
#   scale_x_continuous(breaks = c(0, .2, .4, .6)) +
#   scale_y_continuous(breaks = seq(0, 1.3, 0.1), limits = c(0, 1.3)) +
#   ylab('Complexity (h)') +
#   xlab('Face Looking (%)') +
#   facet_wrap(~Pixelated2)

# Option 1 
pp1 = model_data %>% select(propFace_movie_groupmeancentered, H, Condition = Pixelated2, yhat1) %>%
  ggplot(data = ., aes(x = propFace_movie_groupmeancentered, y=H, group_by(Condition), color = Condition) ) + # group_by(age_bin), color = age_bin)
  geom_point(alpha = .3) + 
  stat_smooth(aes(y = yhat1), method = 'glm', se = TRUE) +
  geom_vline(xintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = seq(-0.4, 0.4, .2)) +
  ylab(expression(alpha)) +
  xlab('Face-Looking (%), Visit-centered') +
  theme_bw()

ggsave(filename = '/Users/sifre002/Box/sifre002/11_Writing/05_DancingLadies_Complexity/figs/2019_06_13_pp1.pdf', 
       plot = pp1, width = 7, height = 5)

# Option 2 
# ggplot(data = model_data, aes(x = propFace_movie_groupmeancentered, y=H, color = Pixelated2, group_by(Pixelated2))) + # group_by(age_bin), color = age_bin)
#   #facet_wrap(~Pixelated2, ncol=1, nrow = 2) +
#   geom_point(alpha = .3) + 
#   geom_vline(xintercept = 0, linetype="dotted") + 
#   geom_smooth(aes(data = model_data, y = yhat1, x = propFace_movie_groupmeancentered, group_by(Pixelated2)),
#               method = 'glm', color = Pixelated2, stat= 'smooth', se = T) +
#   scale_x_continuous(breaks = seq(-0.4, 0.6, .2), limits = c(-.4,.4)) +
#   ylab('Y-hat, Complexity (h)') +
#   xlab('Prop face looking movie, Centered on person-mean') 


ggplot(data = model_data, aes(x = propFace_movie_groupmeancentered, y=H, group_by(Pixelated2))) + 
  geom_point(alpha = .3, aes(color = Pixelated2)) + 
  geom_smooth(inherit.aes = FALSE, aes(x = propFace_movie_groupmeancentered, y = yhat1, group_by(Pixelated2)),
              method = 'glm', color = Pixelated2, stat= 'smooth', se = T) +
    geom_vline(xintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = seq(-0.4, 0.6, .2), limits = c(-.4,.4)) +
  ylab('Y-hat, Complexity (h)') +
  xlab('Prop face looking movie, Centered on person-mean')

ggsave(filename = '/Users/sifre002/Box/sifre002/11_Writing/05_DancingLadies_Complexity/figs/Opt1.pdf', 
       plot = p1, width = 7, height = 5)

ggsave(filename = '/Users/sifre002/Box/sifre002/11_Writing/05_DancingLadies_Complexity/figs/Opt2.pdf', 
       plot = p2, width = 7, height = 5)

```

Simple slopes analysis
```{r}
library (jtools)
library(ggstance)
library(cowplot)
# need to remove cohort var 



ss = sim_slopes(lmer.6b, data=model_data, pred = propFace_movie_groupmeancentered, 
                modx = Pixelated, johnson_neyman = FALSE)
plot(ss)

ss2 = sim_slopes(lmer.6b, pred = propFace_movie_groupmeancentered, 
                modx = Pixelated, 
                johnson_neyman = TRUE, jnplot = TRUE)

plot(ss2)

johnson_neyman(lmer.temp, pred = propFace_movie_groupmeancentered, modx = Pixelated, alpha = 0.05)

ss3 = probe_interaction(lmer.6b, pred = propFace_movie_groupmeancentered, modx = Pixelated, 
                  alpha = .05)

```

Examine model assumptions
```{r}
require(psych)

# 1.The random effects have a multivariate normal distribution
# RE for Visit-level
RE=as.data.frame(ranef(lmer.6b)[1])
sm.density(RE$`ID..Intercept.`, xlab="Random intercepts, visit-level", model="normal")
sm.density(RE$ID.Pixelated1, xlab="RE Pix, visit-level", model="normal")

# RE for Participant 
RE=as.data.frame(ranef(lmer.6b)[2])
sm.density(RE$Participant..Intercept., xlab="Random intercepts, person-level", model="normal")
sm.density(RE$Participant.Age_centeredGrandmean, xlab="RE Pix, person-level", model="normal")

# RE for Movie (there is basically none )
RE=as.data.frame(ranef(lmer.6b)[3])
sm.density(RE$X.Intercept., xlab="Random intercepts", model="normal")

# 2.The errors are normally distributed with a mean of zero
res <- resid(lmer.6b) 

sm.density(res, xlab="Individual residuals", model="normal")
# qqnorm(resid(mixed.lmer))
# qqline(resid(mixed.lmer))

#3.Errors should be independent of each other 
library(broom)
out=augment(lmer.6b)
plot(out$Age,out$.res,xlab="Age",ylab="Residual", xaxt='n')
plot(out$propFace_session_groupmeancentered,
     out$.res,xlab="Prop Face",ylab="Residual", xaxt='n')

options(na.action="na.exclude")
model_data$yhat1 = predict(lmer.6b, newdata = model_data, re.form = NA) 
#Effect size=18.4% var explained --goes down by 2% w/out miss/interp cutoffs
	R = cor(x = model_data$H, 
              y =(model_data$yhat), use = "complete.obs")
	
	R^2 #20.8% of var accounted for by the model

```












# Age vs H (pulling final model from paper)
```{r}
lmer.final =  lmer(H~1+Age_centeredGrandmean +
                # QC 
                AveAge_person + 
                 precision_session_groupmeancentered + precision_person_grandmeancentered + 
                # Variables we care about
                Pixelated + Calver +
                  Age_centeredGrandmean*Pixelated +Age_centeredGrandmean*Calver + 
                (1+Age_centeredGrandmean|Participant) + (1+Pixelated+Calver|ID)+(1|MovieName), data=data, REML=FALSE) 

data$yhat = predict(lmer.final, data)
data$Pixelated = as.factor(data$Pixelated)

# Plot model
p1 = ggplot(data = data %>% filter(Calver == 0), aes(x = Age, y = yhat, group_by(Pixelated), color = Pixelated)) + 
  geom_smooth(method = 'lm', se=FALSE) + 
  theme_bw() + 
  scale_x_continuous(breaks = c(3, 6, 9, 12, 15, 18, 24, 30, 36)) + 
  scale_y_continuous(breaks = c(.6,.7,.8,.9, 1.0), limits = c(0.7, 1.05)) +
  xlab("Age (months)") + 
  ylab("H") + 
  theme(text = element_text(size = 14))
#ggsave(plot = p1, filename = '/Users/sifre002/Box/sifre002/4_Fellowships/2020_DDF/PixEffect.jpg', width=5.0,height=2.5)

```

